Functional trait data tell new story about biodiversity change

### 2021-02-11 paper/manuscript.Rmd
Update intro

Ecological communities are experiencing unprecedented change as a result
of anthropogenic pressures such as climate change, land use change, and
invasive species.

>>>>

Change is a fundamental process shaping ecological communities across
the globe. Natural background rates of change are also now punctated by
shifts as a result of anthropogenic pressures such as climate change,
land use change, and invasive species. One of the most widely accepted
phenomena characterizing the world's ecological communities is that of
change.

Ecological communities are experiencing unprecedented change as a result
of anthropogenic pressures such as climate change, land use change, and
invasive species. Impacts of these pressures are well documented in an
accelerating global extinction rate (citation), shifts in the nature of
well studied systems (natural history sense, e.g. forests (FIA), coral
bleaching?), increasing fragmentation etc (how do we know things are
bad??). Despite all this, a developing body of work indicates that one
of the most ubiquitous metrics of an local-scale ecosystem, the number
of species, does not show a clear global decline. How do we reconcile
documented change in communities with this finding? We assess/make the
case for/present a powerful alternative approach to understanding
biodiveristy change through a functional lens by assess functional
change through time for mammal, bird, and amphibian communities across
the globe.

The number of species (species richness) is the defualt approach for
measuring community structure, especially in studies comparing trends
across many assemblages of different types.
